ABM simulating short-term mating behaviors

### 2022-07-21 submission/manuscript.Rmd
edit for resubmission to JSR, close #24

---
output:
  pdf_document:
    keep_tex: true
  word_document: true
geometry: margin=1.0in
fontsize: 11pt
numbersections: true
bibliography: reference.bib
csl: evolution-and-human-behavior.csl
header-includes:
  - \newcommand{\bcenter}{\begin{center}}
  - \newcommand{\ecenter}{\end{center}}
  - \newcommand{\btitlepage}{\begin{titlepage}}
  - \newcommand{\etitlepage}{\end{titlepage}}
  - \usepackage{setspace}\doublespacing
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{booktabs}
  - \usepackage[font=small,labelfont=bf]{caption}
---

@@

# Abstract {-}

@@

# Introduction

@@

## Gender differences in short-term mating preferences

@@

## Constraints on men's preferences for short-term mating

@@

## A simple model of short-term mating behaviors

@@

We formulated the following hypotheses: assuming gender differences in preferences for short-term mating, 1) there would be no gender differences in short-term mating behaviors between heterosexual men and women when considering the full population, 2) a smaller proportion of heterosexual men (vs. heterosexual women) would have ever engaged in short-term mating, 3) in a population of heterosexual individuals who had any short-term mating, men would have a higher average number of short-term mating behaviors than women, 4) gay men would engage in more short-term mating behaviors compared to lesbian women, and 5) compared to heterosexual men.

# Material and methods

## Model Design

@@

## Experiment Design

@@

## Model Schedule

### Initial setup
In total, 150 women and 150 men were created on the lattice at random locations. All agents were initialized with (1) a three-unit maximum distance by which agents can move away from their birthplace (movement range); (2) a 10% likelihood of two agents forming a long-term relationship upon meeting; (3) single status and no long-term partner; (4) a mate value, sampled from a Gaussian distribution (*M* = 5.0, *SD* = 1.5); (5) no short-term mate or short-term mating history.

@@

### Procedures
#### Procedures for heterosexual agents.
At each time step, agents first checked whether they were in a long-term relationship. If they were in a long-term relationship, they did not move. If they were not in a long-term relationship, they set their heading randomly (if they were within the movement range from the birthplace) or faced the birthplace (if they were out of the movement range from the birthplace) and moved by a random distance. The random distance was less than half of the movement range. Then, the agents decided on whether to engage in short-term mating using the predetermined likelihood (either 25% or 40%).

@@

#### Procedures for gay men and lesbian women agents.
At each time step, men and women moved and decided on short-term mating as the agents did in the heterosexual case. Half of the agents (75 men and 75 women) were also given an initiator status. The initiators checked to see whether there were other agents at the same location. The rest of the procedures were identical to the heterosexual procedures, except that the agents only chose those with the same gender as potential short-term mates or long-term partners.

## Simulations
The model was run for 1,000 time steps in each simulation. We ran 10,000 simulations for each experiment, including 2,500 simulations for each condition. We controlled for initializing random seeds in the model runs. All simulations were run using Netlogo 6.2.1 [@wilensky_1999].

## Statistical analyses
Statistical analyses were conducted using `r R.version.string %>% str_replace(" \\(.*\\)", "")` [@r] and the figures were generated by the ggplot2 package [@ggplot2]. Two-tailed independent samples *t*-tests were used for all statistical comparisons. The data were assumed to be normally distributed within each condition.

# Results

## Gender differences in short-term mating behaviors in the full population

@@

@@

## Heterosexual individuals in the mating pool

@@

## Comparing heterosexual and gay men

@@

## Experimental conditions giving rise to gender differences in short-term mating behaviors

@@

@@

# Discussion

@@

# Conclusion

@@

# Acknowledgements

@@

# Data availability

@@

# References {-}

>>>>

---
output:
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
  word_document: true
mainfont: Times New Roman
geometry: margin=1.0in
fontsize: 12pt
bibliography: reference.bib
csl: evolution-and-human-behavior.csl
header-includes:
  - \newcommand{\bcenter}{\begin{center}}
  - \newcommand{\ecenter}{\end{center}}
  - \newcommand{\btitlepage}{\begin{titlepage}}
  - \newcommand{\etitlepage}{\end{titlepage}}
  - \usepackage{setspace}\doublespacing
  - \usepackage{booktabs}
  - \usepackage[font=small,labelfont=bf]{caption}
---

@@

**Abstract**

@@

**Introduction**

@@

***Gender Differences in Short-term Mating Preferences***

@@

***Constraints on Men's Preferences for Short-term Mating***

@@

***A Simple Model of Short-term Mating Behaviors***

@@

The present study contributed to the existing literature by explicitly investigating the causal consequences of mating preferences on mating behaviors. It also compared heterosexual and gay men's mating behaviors under the same set of assumptions regarding preferences. We formulated the following hypotheses: assuming gender differences in preferences for short-term mating, 1) there would be no gender differences in short-term mating behaviors between heterosexual men and women when considering the full population, 2) a smaller proportion of heterosexual men (vs. heterosexual women) would have ever engaged in short-term mating, 3) in a population of heterosexual individuals who had any short-term mating, men would have a higher average number of short-term mating behaviors than women, 4) gay men would engage in more short-term mating behaviors compared to lesbian women, and 5) compared to heterosexual men.

\vspace{5mm}

**Materials and Methods**

***Model Design***

@@

***Experiment Design***

@@

***Model Schedule***

*Initial Setup*

In total, 150 women and 150 men were created on the lattice at random locations. All agents were initialized with (1) a three-unit maximum distance by which agents can move away from their birthplace (movement range); (2) a 10% likelihood of two agents forming a long-term relationship upon meeting; (3) single status and no long-term partner; (4) a mate value, sampled from a Gaussian distribution (*M* = 5.0, *SD* = 1.5); (5) no short-term mate or short-term mating history.

@@

*Procedures*

***Procedures for heterosexual agents.*** At each time step, agents first checked whether they were in a long-term relationship. If they were in a long-term relationship, they did not move. If they were not in a long-term relationship, they set their heading randomly (if they were within the movement range from the birthplace) or faced the birthplace (if they were out of the movement range from the birthplace) and moved by a random distance. The random distance was less than half of the movement range. Then, the agents decided on whether to engage in short-term mating using the predetermined likelihood (either 25% or 40%).

@@

***Procedures for gay men and lesbian women agents.*** At each time step, men and women moved and decided on short-term mating as the agents did in the heterosexual case. Half of the agents (75 men and 75 women) were also given an initiator status. The initiators checked to see whether there were other agents at the same location. The rest of the procedures were identical to the heterosexual procedures, except that the agents only chose those with the same gender as potential short-term mates or long-term partners.

***Simulations***

The model was run for 1,000 time steps in each simulation. We ran 10,000 simulations for each experiment, including 2,500 simulations for each condition. We controlled for initializing random seeds in the model runs. All simulations were run using Netlogo 6.2.1 [@wilensky_1999].

***Statistical Analyses***

Statistical analyses were conducted using `r R.version.string %>% str_replace(" \\(.*\\)", "")` [@r] and the figures were generated by the ggplot2 package [@ggplot2]. Two-tailed independent samples *t*-tests were used for all statistical comparisons. The data were assumed to be normally distributed within each condition.

\vspace{5mm}

**Results**

***Gender Differences in Short-term Mating Behaviors in the Full Population***

@@

[Figure 1 near here]

@@

***Heterosexual Individuals in the Mating Pool***

@@

[Figure 2 near here]

***Comparing Heterosexual and Gay Men***

@@

[Figure 3 near here]

***Experimental Conditions Giving Rise to Gender Differences in Short-term Mating Behaviors***

@@

[Table 1 near here]

@@

[Table 2 near here]

\vspace{5mm}

**Discussion**

@@

\vspace{5mm}

**Conclusion**

@@

\vspace{5mm}

**Acknowledgements**

@@

\vspace{5mm}

**Declaration of Competing Interest**

We declare that there are no known competing interests that might have influenced the work reported in this paper.

\vspace{5mm}

**Data Availability**

@@

**References**

### 2022-07-21 submission/manuscript.tex
edit for resubmission to JSR, close #24

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  11pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\newcommand{\bcenter}{\begin{center}}
\newcommand{\ecenter}{\end{center}}
\newcommand{\btitlepage}{\begin{titlepage}}
\newcommand{\etitlepage}{\end{titlepage}}
\usepackage{setspace}\doublespacing
\usepackage{helvet}
\renewcommand*\familydefault{\sfdefault}
\usepackage{booktabs}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\hypertarget{abstract}{%
\section*{Abstract}\label{abstract}}
\addcontentsline{toc}{section}{Abstract}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{gender-differences-in-short-term-mating-preferences}{%
\subsection{Gender differences in short-term mating
preferences}\label{gender-differences-in-short-term-mating-preferences}}

@@

\hypertarget{constraints-on-mens-preferences-for-short-term-mating}{%
\subsection{Constraints on men's preferences for short-term
mating}\label{constraints-on-mens-preferences-for-short-term-mating}}

@@

\hypertarget{a-simple-model-of-short-term-mating-behaviors}{%
\subsection{A simple model of short-term mating
behaviors}\label{a-simple-model-of-short-term-mating-behaviors}}

@@

We formulated the following hypotheses: assuming gender differences in
preferences for short-term mating, 1) there would be no gender
differences in short-term mating behaviors between heterosexual men and
women when considering the full population, 2) a smaller proportion of
heterosexual men (vs.~heterosexual women) would have ever engaged in
short-term mating, 3) in a population of heterosexual individuals who
had any short-term mating, men would have a higher average number of
short-term mating behaviors than women, 4) gay men would engage in more
short-term mating behaviors compared to lesbian women, and 5) compared
to heterosexual men.

\hypertarget{material-and-methods}{%
\section{Material and methods}\label{material-and-methods}}

\hypertarget{model-design}{%
\subsection{Model Design}\label{model-design}}

@@

\hypertarget{experiment-design}{%
\subsection{Experiment Design}\label{experiment-design}}

@@

\hypertarget{model-schedule}{%
\subsection{Model Schedule}\label{model-schedule}}

\hypertarget{initial-setup}{%
\subsubsection{Initial setup}\label{initial-setup}}

@@

\hypertarget{procedures}{%
\subsubsection{Procedures}\label{procedures}}

\hypertarget{procedures-for-heterosexual-agents.}{%
\paragraph{Procedures for heterosexual
agents.}\label{procedures-for-heterosexual-agents.}}

At each time step, agents first checked whether they were in a long-term
relationship. If they were in a long-term relationship, they did not
move. If they were not in a long-term relationship, they set their
heading randomly (if they were within the movement range from the
birthplace) or faced the birthplace (if they were out of the movement
range from the birthplace) and moved by a random distance. The random
distance was less than half of the movement range. Then, the agents
decided on whether to engage in short-term mating using the
predetermined likelihood (either 25\% or 40\%).

@@

\hypertarget{procedures-for-gay-men-and-lesbian-women-agents.}{%
\paragraph{Procedures for gay men and lesbian women
agents.}\label{procedures-for-gay-men-and-lesbian-women-agents.}}

At each time step, men and women moved and decided on short-term mating
as the agents did in the heterosexual case. Half of the agents (75 men
and 75 women) were also given an initiator status. The initiators
checked to see whether there were other agents at the same location. The
rest of the procedures were identical to the heterosexual procedures,
except that the agents only chose those with the same gender as
potential short-term mates or long-term partners.

\hypertarget{simulations}{%
\subsection{Simulations}\label{simulations}}

@@

\hypertarget{statistical-analyses}{%
\subsection{Statistical analyses}\label{statistical-analyses}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{gender-differences-in-short-term-mating-behaviors-in-the-full-population}{%
\subsection{Gender differences in short-term mating behaviors in the
full
population}\label{gender-differences-in-short-term-mating-behaviors-in-the-full-population}}

@@

@@

\hypertarget{heterosexual-individuals-in-the-mating-pool}{%
\subsection{Heterosexual individuals in the mating
pool}\label{heterosexual-individuals-in-the-mating-pool}}

@@

\hypertarget{comparing-heterosexual-and-gay-men}{%
\subsection{Comparing heterosexual and gay
men}\label{comparing-heterosexual-and-gay-men}}

@@

\hypertarget{experimental-conditions-giving-rise-to-gender-differences-in-short-term-mating-behaviors}{%
\subsection{Experimental conditions giving rise to gender differences in
short-term mating
behaviors}\label{experimental-conditions-giving-rise-to-gender-differences-in-short-term-mating-behaviors}}

@@

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

@@

\hypertarget{data-availability}{%
\section{Data availability}\label{data-availability}}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\newcommand{\bcenter}{\begin{center}}
\newcommand{\ecenter}{\end{center}}
\newcommand{\btitlepage}{\begin{titlepage}}
\newcommand{\etitlepage}{\end{titlepage}}
\usepackage{setspace}\doublespacing
\usepackage{booktabs}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\textbf{Abstract}

@@

\textbf{Introduction}

@@

\textbf{\emph{Gender Differences in Short-term Mating Preferences}}

@@

\textbf{\emph{Constraints on Men's Preferences for Short-term Mating}}

@@

\textbf{\emph{A Simple Model of Short-term Mating Behaviors}}

@@

The present study contributed to the existing literature by explicitly
investigating the causal consequences of mating preferences on mating
behaviors. It also compared heterosexual and gay men's mating behaviors
under the same set of assumptions regarding preferences. We formulated
the following hypotheses: assuming gender differences in preferences for
short-term mating, 1) there would be no gender differences in short-term
mating behaviors between heterosexual men and women when considering the
full population, 2) a smaller proportion of heterosexual men
(vs.~heterosexual women) would have ever engaged in short-term mating,
3) in a population of heterosexual individuals who had any short-term
mating, men would have a higher average number of short-term mating
behaviors than women, 4) gay men would engage in more short-term mating
behaviors compared to lesbian women, and 5) compared to heterosexual
men.

\vspace{5mm}

\textbf{Materials and Methods}

\textbf{\emph{Model Design}}

@@

\textbf{\emph{Experiment Design}}

@@

\textbf{\emph{Model Schedule}}

\emph{Initial Setup}

@@

\emph{Procedures}

\textbf{\emph{Procedures for heterosexual agents.}} At each time step,
agents first checked whether they were in a long-term relationship. If
they were in a long-term relationship, they did not move. If they were
not in a long-term relationship, they set their heading randomly (if
they were within the movement range from the birthplace) or faced the
birthplace (if they were out of the movement range from the birthplace)
and moved by a random distance. The random distance was less than half
of the movement range. Then, the agents decided on whether to engage in
short-term mating using the predetermined likelihood (either 25\% or
40\%).

@@

\textbf{\emph{Procedures for gay men and lesbian women agents.}} At each
time step, men and women moved and decided on short-term mating as the
agents did in the heterosexual case. Half of the agents (75 men and 75
women) were also given an initiator status. The initiators checked to
see whether there were other agents at the same location. The rest of
the procedures were identical to the heterosexual procedures, except
that the agents only chose those with the same gender as potential
short-term mates or long-term partners.

\textbf{\emph{Simulations}}

@@

\textbf{\emph{Statistical Analyses}}

@@

\vspace{5mm}

\textbf{Results}

\textbf{\emph{Gender Differences in Short-term Mating Behaviors in the
Full Population}}

@@

{[}Figure 1 near here{]}

@@

\textbf{\emph{Heterosexual Individuals in the Mating Pool}}

@@

{[}Figure 2 near here{]}

\textbf{\emph{Comparing Heterosexual and Gay Men}}

@@

{[}Figure 3 near here{]}

\textbf{\emph{Experimental Conditions Giving Rise to Gender Differences
in Short-term Mating Behaviors}}

@@

{[}Table 1 near here{]}

@@

{[}Table 2 near here{]}

\vspace{5mm}

\textbf{Discussion}

@@

\vspace{5mm}

\textbf{Conclusion}

@@

\vspace{5mm}

\textbf{Acknowledgements}

@@

\vspace{5mm}

\textbf{Declaration of Competing Interest}

We declare that there are no known competing interests that might have
influenced the work reported in this paper.

\vspace{5mm}

\textbf{Data Availability}

@@

\textbf{References}

### 2022-07-21 submission/title_page.Rmd
edit for resubmission to JSR, close #24

---
output:
  pdf_document
geometry: margin=1.0in
fontsize: 11pt
header-includes:
  - \newcommand{\bcenter}{\begin{center}}
  - \newcommand{\ecenter}{\end{center}}
  - \newcommand{\btitlepage}{\begin{titlepage}}
  - \newcommand{\etitlepage}{\end{titlepage}}
  - \usepackage{setspace}\doublespacing
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
---

@@

**Declaration of Competing Interest:** We declare that there are no known competing interests that might have influenced the work reported in this paper.

>>>>

---
output:
  pdf_document:
    latex_engine: xelatex
mainfont: Times New Roman
geometry: margin=1.0in
fontsize: 12pt
header-includes:
  - \newcommand{\bcenter}{\begin{center}}
  - \newcommand{\ecenter}{\end{center}}
  - \newcommand{\btitlepage}{\begin{titlepage}}
  - \newcommand{\etitlepage}{\end{titlepage}}
  - \usepackage{setspace}\doublespacing
---

@@
